### 2012-06-18 inst/examples/value_of_information_allee.Rmd
allee example with table

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties)), caption="Mean realized net present value over simulations"), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties)), caption="Standard deviation in realized net present value over simulations"), type="html")
````
